Active Learning from Blackbox to Timed Connectors

### 2016-01-12 paper/paper.tex
.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{./images/IoT.png}
  \end{center}
  \caption{Inter of Things in Our Life}
  \label{fig:IoT}
\end{figure}

researchers have been focusing on this area, and come up with a series of impressive works.
\todo{a list}
However, most of these works are based on models, instead of binaries. Then it comes a well-known
problem: \emph{how can we obtain these models?}

\emph{Correctness} of connectors is very much related to some low-level implementation details.
For example, well-writen code may behave dramatically weird with an improper set of concurrency
primitives. Such things happen frequently in embedded systems with different hardware platforms or
operating systems. Consequently, manually modeling a existing connector seems rather unreliable,
even with reference to its source code.

In this paper, we proposed a active learning framework to automatically extract timed connectors
from blackbox models.

@@

% it seems that we need a graph to describe how we're doing this work
\todo{better graph}
% \input{images/flow.tex}

In this paper, we presented an adapted active learning algorithm to extract timed Reo connectors
from binaries with no source code needed.

\section{Preliminaries}

\subsection{Reo Coordination Language} 
\label{sec:reo}
We provide here a brief overview of the main concepts of Reo, more details can be found in
\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.

@@

@@

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) The name comes from
    some grammar-learning papers (e.g. \cite{DBLP:journals/iandc/Angluin87}), where \emph{mq} checks
    if a word is a member of certain language defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide simulation results for given input
    sequences.
    \todo{example, also a mealy-machine example}
  \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed.
\end{itemize}

@@

\section{Timed Connectors as Mealy Machines}

\subsection{External Behavior of Reo Connectors}
So far as we can tell, most
works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

@@

\section{Experiments} 
Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in
Golang\cite{golang}.

>>>>

\emph{Timed Reo} is a real-time extension of the coordination language \emph{Reo}. With timeline
involved, coordination process in DRES can be depicted clearly and intuitively. Different formal
semantics are proposed to specify the behavior of timed Reo.
For example, in \cite{DBLP:conf/tase/Meng12}, a UTP-based
(\emph{Unifying Theories of Programming}) semantics is provided to verify connectors as
\emph{designs}. An operational semantics based on \emph{constraint automata} was raised by Baier et
al., where a variant of LTL was also proposed to describe the properties of timed connectors.

Formal verification techniques have also been proved applicable in timed connectors.
\cite{DBLP:conf/tase/LiCWS15} has shown us a comformance testing method on timed connectors.
Bounded model checking methods were also adapted in \cite{DBLP:journals/scp/Kemper12}, based on SAT
solvers. All these solutions seem practical and impressive, however, a common question is faced by
most of them, which is: \emph{How to obtain these formal models?}

\emph{Correctness} of connectors is very much related to some low-level implementation details.
For example, well-writen code may behave dramatically weird with an improper set of concurrency
primitives. Such things happen frequently in embedded systems with different hardware platforms or
operating systems. Consequently, manually modeling an existing connector seems rather unreliable,
even with reference to its source code.

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.4\textwidth]{./images/howto.png}
  \end{center}
  \caption{The Active Learning Framework}
  \label{fig:howto}
\end{figure}

In this paper, we proposed a active learning framework (shown in Figure \ref{fig:howto}) to
automatically extract timed connectors from blackbox models.

@@

\todo{finish this part!}

The paper is structured as follows. After this general introduction, in Section
\ref{sec:preliminaries} we briefly illustrate some basic concepts, including Reo the coordination
language, Mealy machine, and active automata learning. Section \ref{sec:semantics} defines the
Mealy-machine-based operational semantics of Reo, which is used in Section \ref{sec:activelearning}
to show how to extract Reo models from blackboxes by means of active learning. Finally, in Section
\ref{sec:experiment}, we discuss the optimization and implementation in \texttt{Golang}.

\section{Preliminaries} 
\label{sec:preliminaries}
\subsection{Reo Coordination Language} 
\label{sec:reo}
We provide here a brief overview of the main concepts of Reo, more details can be found in
\cite{DBLP:journals/mscs/Arbab04, DBLP:journals/scp/BaierSAR06}.

@@

\todo{supplementation}

@@

\begin{itemize}
  \item[-] \textbf{Membership Query} (hereinafter referred to as \emph{mq}) The name comes from
    some grammar-learning papers (e.g. \cite{DBLP:journals/iandc/Angluin87}), where \emph{mq} checks
    if a word is a member of certain language defined by the given grammar. When it comes to
    automata learning, \emph{mq} is supposed to provide \emph{simulation results} for given input
    sequences.
  \item[-] \textbf{Equivalence Query} (hereinaftr referred to as \emph{eq}) Given a hypothesis
    (usually constructed by the learning algorithm), \emph{eq} checks whether the hypothesis is
    equivalent to the system-under-learn and generates a counter-example if needed. Generally, 
    \emph{equivalence query} is irrealizable when SUT is a blackbox. So we tactically use membership
    queries to achieve the approximate results.
\end{itemize}

@@

\section{Timed Connectors as Mealy Machines}
\label{sec:semantics}
\subsection{External Behavior of Reo Connectors}
So far as we can tell, most
works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

@@

\section{Experiments} 
\label{sec:experiment}

Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in
Golang\cite{golang}.
